30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-12 paper.tex
Cleared up some weird sentence structures

			In contrast to Tor, MorphMix does not feature a centralized node discovery. Instead, every node is free to chose a set of next nodes that will be the continuation of the anonymous tunnel. A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel. To prevent this, a witness node is appointed to mediate the setup of the anonymous tunnel. Although this makes the possibility of such an attack more difficult, it is not impossible.

>>>>

			In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism. Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel. A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel. To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel. Although this makes the possibility of such an attack more difficult, it is not impossible.
